PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-21 qfenv_paper/qf_environment.tex
zcosmos degrees

The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment. The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$. We also adjusted the environment classification thresholds for these analyses. The results obtained from using different apertures and environment classification thresholds are consistent with the results presented below.

@@

To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample. First, using \texttt{ransack} from \cite{Swanson:2008aa}, we construct a random sample of  $N_{\rm{ransack}} = 1,000,000$ points with $RA$ and $Dec$ randomly selected within the window function of the EDP (SDSS EDP and PRIMUS EDP separately). We then compute the angular separation, $\theta_{i, \rm{ap}}$ that corresponds to $R_{\rm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$. For each sample galaxy we count the number of \texttt{ransack} points within $\theta_{i, \rm{ap}}$ of the galaxy: $n_{i,\rm{ransack}}$. Afterwards, we compare $n_{i,\rm{ransack}}$ to the expected value computed from the angular area of the environment defining aperture and the EDP window function: 
\begin{equation} \label{eq:ransack}
<n_{\rm{ransack}}>_{i} = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
\end{equation} 
$A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off. For $R_{\rm{ap}}= 2\;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$. If $n_{i, \rm{ransack}} > E_{i}[n_{\rm{ransack}}]$ then galaxy $i$ remains in our sample; otherwise, it is discarded.

@@

\cite{Kovac:2014aa} finds a similar environment dependence on the total $f_{\rm{Q}}$ evolution to our results, with a greater $f_{\rm{Q}}$ evolution for high density environments. Unfortunately, contrary to our results, \cite{Kovac:2014aa} finds that $f_{\rm{Q}}$ decreases for both environments over cosmic time. The negative slope of the $f_{\rm{Q}}$ evolution is enhanced in Figure \ref{fig:qffit_comp} due to the galaxy classification correction we impose. However even without the correction (not shown), in their best-fit values, \cite{Kovac:2014aa} finds a decreasing $f_{\rm{Q}}$ evolution. 
%Discuss possible reasons for the difference between zCOSMOS results and our results. Point out the sample sizes and square degree coverage.

>>>>

The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \:h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25 \:h^{-1}\rm{Mpc}$ to measure environment. The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \:h^{-1}\rm{Mpc}$. We also adjusted the environment classification thresholds for these analyses. The results obtained from using different apertures and environment classification thresholds are consistent with the results presented below.

@@

To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample. First, using \texttt{ransack} from \cite{Swanson:2008aa}, we construct a random sample of  $N_{\rm{ransack}} = 1,000,000$ points with $RA$ and $Dec$ randomly selected within the window function of the EDP (SDSS EDP and PRIMUS EDP separately). We then compute the angular separation, $\theta_{i, \rm{ap}}$ that corresponds to $R_{\rm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$. For each sample galaxy we count the number of \texttt{ransack} points within $\theta_{i, \rm{ap}}$ of the galaxy: $n_{i,\rm{ransack}}$. Afterwards, we compare $n_{i,\rm{ransack}}$ to the expected value computed from the angular area of the environment defining aperture and the EDP window function: 
\begin{equation} \label{eq:ransack}
<n_{\rm{ransack}}>_{i} = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
\end{equation} 
$A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off. For $R_{\rm{ap}}= 2\;h^{-1} \rm{Mpc}$, $f_{\rm{thresh}} = 0.75$. If $n_{i, \rm{ransack}}$ is greater than $<n_{\rm{ransack}}>_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded.

@@

\cite{Kovac:2014aa} finds a similar environment dependence on the total $f_{\rm{Q}}$ evolution to our results, with a greater $f_{\rm{Q}}$ evolution for high density environments. Unfortunately, contrary to our results, \cite{Kovac:2014aa} finds that $f_{\rm{Q}}$ decreases for both environments over cosmic time. The negative slope of the $f_{\rm{Q}}$ evolution is enhanced in Figure \ref{fig:qffit_comp} due to the galaxy classification correction we impose. However even without the correction (not shown), in their best-fit values, \cite{Kovac:2014aa} finds a decreasing $f_{\rm{Q}}$ evolution. 
%Discuss possible reasons for the difference between zCOSMOS results and our results. Point out the sample sizes and square degree coverage. 
% Kovac: 1.7 deg^2, 0.1 < z < 0.4 2340 and 0.4 < z < 0.7 2448. Most of the data points have errors of +/- 0.1, at least +/-0.05
% Iovino: 1.7 deg^2  617 galaxies in 10.3 < M < 10.8 and 0.1 < z < 0.6. Errors are +/1 0.1
